Artin Group Presentations of Reflection Groups

### 2014-07-19 Paper.tex
correctly capitalized Artin -aaron

In order to prove our main result, Theorem ~\ref{thm:main}, we must first define the Artin Group associated to a finite type diagram. This definition will be similar to that made in \cite{BM13} at the beginning of Section 3, except that we shall not require $s_i^2 = e.$ Since artin groups are very similar to coxeter groups, with the caveat that the generators are not involutions, we will be able to use these modified relations to great effect.

@@

For $\Gamma$ a diagram of finite type, we define the associated Artin Group as follows. The associated artin group $W_\Gamma$ is generated by $s_i,$ where there is one $s_i$ for each vertex $i$ in $\Gamma.$ These generators are subject to the following relations
\begin{itemize}
	\item[(R2)] With $m_{ij}$ as defined in ~\ref{mij_defn}, for all $i \neq j,$ we add the relations
	$\langle s_i,s_j \rangle^{m_{ij}}= \langle s_j,s_i \rangle^{m_{ij}}.$

>>>>

In order to prove our main result, Theorem ~\ref{thm:main}, we must first define the Artin Group associated to a finite type diagram. This definition will be similar to that made in \cite{BM13} at the beginning of Section 3, except that we shall not require $s_i^2 = e.$ Since Artin Groups are very similar to coxeter groups, with the caveat that the generators are not involutions, we will be able to use these modified relations to great effect.

@@

For $\Gamma$ a diagram of finite type, we define the associated Artin Group as follows. The associated Artin group $W_\Gamma$ is generated by $s_i,$ where there is one $s_i$ for each vertex $i$ in $\Gamma.$ These generators are subject to the following relations
\begin{itemize}
	\item[(R2)] With $m_{ij}$ as defined in ~\ref{mij_defn}, for all $i \neq j,$ we add the relations
	$\langle s_i,s_j \rangle^{m_{ij}}= \langle s_j,s_i \rangle^{m_{ij}}.$
